Paper_analyses

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
main ideas of the paper are down
Update Paper_Analyses_subj_obje_arousal.Rmd

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor,color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence))+

@@

@@

@@

pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

@@

@@

@@

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

@@

hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

@@

hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif_c* valence_c+
                                         (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier"))
# arousal_c
summary(hr_dif_models$valfrom_hr)

hr_dif_models$valfrom_hr_ar <- lmer(valence_c ~   Bio_Mean_HR_dif_c * arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier"))
# arousal_c
summary(hr_dif_models$valfrom_hr_ar)

@@

hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   + valence_c+
                                        + (1 | ssid)+
                                     (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_ar_vl)

@@

@@

car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          # point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

@@

# Visualize: Specify the comparisons you want
my_comparisons <- list( c("1", "2"), c("1", "3"), c("2", "3") )
my_comparisons <- list( c("mixed", "highlyarousing_aitated"), c("mixed", "calmish"), c("highlyarousing_aitated", "calmish") )
clustering_agg$cluster_interpreted
library(ggpubr)
ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ArousalMean",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)     # Add global p-value

@@

@@

Let's do on the unnagregates data

>>>>

tmp.df4_full_stim_downs_jun2021_60bins_no_na<- subset(tmp.df4_full_stim_downs_jun2021_60bins, !is.na(stimDescription))
nrow(tmp.df4_full_stim_downs_jun2021_60bins_no_na)

nrow(tmp.df4_full_stim_downs_jun2021_60bins)

tmp.df4_full_stim_downs_jun2021_60bins_no_na$stimIAPS2<- substr(tmp.df4_full_stim_downs_jun2021_60bins_no_na$stimIAPS, 1,4)

left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)%>%
# tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor,color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence))+

@@

tmp.df4_full_stim_downs_jun2021_60bins_no_na<- left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)
# plot with clusters
# left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)%>%
# tmp.df4_full_stim_downs_jun2021_60bins %>%
  # subset(!is.na(ground_arousal_lab))%>%
tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  ggplot(aes(x = timerezero3, y = pup_basCor,color = cluster_interpreted, linetype = cluster_interpreted))+

 # stat_summary(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence), fun = mean,geom = "line", size = 1.5)
 #  
  # stat_smooth(aes(group= mediansplit_ground_arousal), fun = mean,geom = "line",
  #              se = F, alpha = 1, size = 1.5)+
  stat_smooth(size=1.5, method = "loess", level = 0.95, 
    fullrange = TRUE, se = FALSE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)
   labs(color  = "mediansplit_ground_arousal", linetype = "mediansplit_ground_valence")
   # facet_grid(~mediansplit_ground_valence)

@@

timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]

timecourse_60bin_result_df %>%
  group_by(p_br_adj_TRUE)%>%
  summarise_at(c("Estimate_br"), mean, na.rm = TRUE)
  mutate(mean_effsize = Estimate_br)

  timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]

 timecourse_60bin_result_df %>%
  group_by(p_ar_adj_TRUE)%>%
  summarise_at(c("Estimate_ar"), mean, na.rm = TRUE)

 # ar and val;
   timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]

 timecourse_60bin_result_df %>%
  group_by(p_ar_vl_adj_TRUE)%>%
  summarise_at(c("Estimate_ar_vl"), median, na.rm = TRUE)

 # valence
  # ar and val;
   timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_vl_adj_TRUE == TRUE]

 timecourse_60bin_result_df %>%
  group_by(p_vl_adj_TRUE)%>%
  summarise_at(c("Estimate_vl"), median, na.rm = TRUE)

@@

db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs<- abs(db_full4new_stim_screen_pupil_nopract_nt_304$arousal)

db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs_z<- scale(db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs, center = TRUE,scale = TRUE)

pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

@@

#

pupil_arousal_findings$BIO_CDA.PhasicMax_ar <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

@@

summary(pupil_arousal_findings$BIO_CDA.PhasicMax_ar)
pupil_arousal_findings$BIO_CDA.PhasicMax_vl <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ valence_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

summary(pupil_arousal_findings$BIO_CDA.PhasicMax_vl)

# deal with colinearity by swicthing predictor to dv

db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax <- log1p(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.PhasicMax+.1)

db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax_z<- scale(db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1]

pupil_arousal_findings$ar_BIO_CDA.PhasicMax <- lmer(arousal_c ~ valence_c +log1p_BIO_CDA.PhasicMax_z+ (1|ssid)+(1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

summary(pupil_arousal_findings$ar_BIO_CDA.PhasicMax)

pupil_arousal_findings$ar_BIO_CDA.PhasicMax <- lmer( valence_c~ arousal_c+log1p_BIO_CDA.PhasicMax_z+ (1|ssid)+(1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

summary(pupil_arousal_findings$ar_BIO_CDA.PhasicMax)

@@

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

@@

hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

@@

db_full6new_hr_fix_stim_nt1.11<- subset(db_full6new_hr_fix_stim_nt1.1, !is.na(stimDescription))

hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif_c* valence_c+
                                         (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier"))
# arousal_c
summary(hr_dif_models$valfrom_hr)

hr_dif_models$valfrom_hr_ar <- lmer(valence_c ~   Bio_Mean_HR_dif_c * arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier"))
# arousal_c
summary(hr_dif_models$valfrom_hr_ar)

@@

db_full6new_hr_fix_stim_nt1.1$arousal_abs<- abs(db_full6new_hr_fix_stim_nt1.1$arousal)
db_full6new_hr_fix_stim_nt1.1$arousal_abs_z<- scale(db_full6new_hr_fix_stim_nt1.1$arousal_abs, center = TRUE,scale = TRUE)

table(is.na(db_full6new_hr_fix_stim_nt1.1$stimDescription))
hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
                                        + (1 | ssid)+
                                     (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_ar_vl)

# abs
hr_dif_models$hr_dif_arabs_vl <- lmer(Bio_Mean_HR_dif~arousal_abs_z   * valence_c+
                                        + (1 | ssid)+
                                     (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_arabs_vl)

@@

  db_full6new_hr_fix_stim_nt1.11%>%
    subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
    group_by(stimIAPS)%>%
    mutate(mean_hr_dif = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
    ggplot(aes(valence_c, mean_hr_dif))+
    # geom_point()+
    stat_summary(aes(y = Bio_Mean_HR_dif),geom = 'pointrange')+
    geom_smooth(method = 'lm', se = F)+
    p$graphstyle

    db_full6new_hr_fix_stim_nt1.11%>%
    subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
    group_by(stimIAPS)%>%
    mutate(mean_hr_dif = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
    ggplot(aes(arousal_abs_z, mean_hr_dif))+
    # geom_point()+
    stat_summary(aes(y = Bio_Mean_HR_dif),geom = 'pointrange')+
    geom_smooth(method = 'lm', se = F)

@@

car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          point = FALSE,
          # ellipsoid = TRUE,
          # surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

@@

# Visualize: Specify the comparisons you want
my_comparisons <- list( c("1", "2"), c("1", "3"), c("2", "3") )
my_comparisons <- list( c("mixed", "highlyarousing_aitated"), c("mixed", "calmish"), c("highlyarousing_aitated", "calmish") )
clustering_agg$cluster_interpreted
library(ggpubr)

ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ArousalMean",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)     # Add global p-value

@@

tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "valence",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

options(scipen = 999)
tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "arousal",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

@@

use the clusters ti fit mixed models

```{r}
View(clustering)

table(is.na(clustering$stimDescription))
table(is.na(clustering2$stimDescription))

clustering2

clustering3<- left_join(clustering2, cluster_stim)

cluster_lmers<- list()
clustering3$stimIAPS2<- as.factor(as.character(clustering3$stimIAPS2))

clustering3$ssid<- as.factor(as.character(clustering3$ssid))
clustering3

library(lmerTest)

clustering3$arousal

cluster_lmers$arousal <- lmer(arousal ~ cluster_interpreted + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

summary(cluster_lmers$arousal)

anova(cluster_lmers$arousal)

emmeans::emmeans(cluster_lmers$arousal, pairwise~cluster_interpreted)

# valence
cluster_lmers$valence <- lmer(valence ~ cluster_interpreted + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

summary(cluster_lmers$valence)
emmeans::emmeans(cluster_lmers$valence, pairwise~cluster_interpreted)

Let's do on the unnagregated data
